Introduction to data

### 2018-08-30 DATA606/Lab1/michael-intro_to_data.Rmd
Work on DATA 606 Lab 1

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

```{r}
dim(cdc)

summary(cdc)
```

**There are 20K records with 9 variables.  height weight wtdesire and age are numeric and continuous. gender and genhlth are categorical.  exerany, hlthplan and smoke100 are categorical (0=no and 1=yes).**

@@

```{r}
summary(cdc$height)
```

```{r}
IQR(cdc$height)
```

```{r}
summary(cdc$age)
```

```{r}
IQR(cdc$age)
```

```{r}
table(cdc$gender) / nrow(cdc)
```

```{r}
table(cdc$exerany) / nrow(cdc)
```

```{r}
nrow(cdc[cdc$gender=="m",])
```

```{r}
nrow(cdc[cdc$genhlth == "excellent",]) / nrow(cdc)
```

@@

**Males are more likely to smoke than females.**

@@

```{r}
under23_and_smoke <- subset(cdc, smoke100 == "1" & age < 23)
```

@@

**The box plot shows the distribution of the data.  It shows the IQR, median, and outliers.  The above box plot shows that the individuals with poorer general health are more likely to have a higher BMI than those with better health.**

```{r}
boxplot(bmi ~ cdc$gender)
```

**I picked gender because general health status was already taken.  I would expect a difference based on the gender because men and women are different.  The plot shows a greater variation among the women than the men.**

@@

```{r}
plot(x = cdc$weight, y = cdc$wtdesire)
abline(lm(cdc$weight ~ cdc$wtdesire), col="#357FAA", lty='longdash', lwd=2)
```

**The relationship is positive.**

@@

```{r}
wdiff <- cdc$wtdesire - cdc$weight
```

@@

**It is a continous variable.  If wdiff is equal to 0 it means that their desired weight is their current weight.  If wdiff is positive they desire to put on weight.  If it is negative they desire to weight less.**

@@

```{r}
library(e1071)
summary(wdiff)
skewness(wdiff)
```

```{r}
hist(wdiff)
```

**The data is left skewed and clustered around -10 to -15.  There is a few extreme values but in generall people want to loose a few pounds.**
